\documentclass[11pt]{article}
\usepackage{mathtools,hyperref,booktabs,fullpage, txfonts}
\usepackage[amssymb,cdot]{SIunits}
\usepackage[utopia]{mathdesign}     

\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{fullpage}
 
\definecolor{lightgray}{gray}{0.93}

\pagestyle{empty}
\setlength\parindent{0pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
 
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}%
                                  {-3.5ex \@plus -1ex \@minus -.2ex}%
                                  {2.3ex \@plus.2ex}%
                                  {\normalfont\bfseries}}
\makeatother


\begin{document}

{\large
  \begin{center}
    {\bf ME 701 -- Development of Computer Applications In Mechanical Engineering \\ 
         Homework 2 }         
  \end{center}
}
 
All submissions must be through GitHub.
Somebody, please remove me!

\section*{Problem 1}

Write a bash script that converts a temperature from degrees Fahrenheit to degrees Celcius. 
One way is to use {\tt bc}; see TLCL for more.  
The script should be called {\tt temperature.sh}.

\section*{Problem 2}
 
Write a bash script that provides a count of the number of files and subdirectories in the current directory. 
Hint: use {\tt grep}.
The script should be named {\tt count\_files\_and\_subdirs.sh}.
\section*{Problem 3}

For this problem, you need to find a partner (or team of partners) in the class.  
You are then to do the following:
\begin{enumerate}
 \item Add your partner's repository as a remote
 \item Fetch and checkout your partners {\tt master} branch as a new branch named {\tt dev} in your own, local repository
 \item Modify your partner's {\tt  temperature.sh} script to output the temperature in Kelvin, too.
 \item Commit any changes and {\tt push} to {\it your} GitHub repository as a new remote branch named {\tt dev}
 \item Make a {\it pull request} from your remote {\tt dev} branch into your partner's {\tt master} branch
 \item Communicate as needed so that the pull request is reviewed and accepted.
\end{enumerate}
For full credit, each of the steps described above must be clearly visible from the commit log!


\end{document}
